\documentclass[12pt]{article}

\usepackage[left=1cm,top=1cm,right=1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[brazil]{babel}
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{array}
\usepackage{palatino}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\usepackage{fontawesome5}

\titleformat
{\section} % command
[display] % shape
{\bfseries\large} % format
{} % label
{\medskip} % sep
{} % before-code
[\hrule] % after-code

\newenvironment{tightlist}
  {\begin{list}
    {$\cdot$}
    {
      \setlength{\leftmargin}{0em}
      \setlength{\itemsep}{\smallskipamount}
    }
  }
{\end{list}}

\begin{document}

\pagestyle{empty}

\centerline{\huge\bf PHELIPE TELES DA SILVA}
\medskip

\centerline{January 30, 1996 $\cdot$ Rio de Janeiro}
\smallskip

\centerline{
  \href{mailto:telesphelipe@gmail.com}{\faIcon[solid]{envelope} telesphelipe@gmail.com}
  $\cdot$
  \href{https://phelipetls.github.io}{\faIcon[solid]{globe} phelipetls.github.io}
  $\cdot$
  \href{https://linkedin.com/in/phelipeteles}{\faIcon[solid]{linkedin} phelipeteles}
  $\cdot$
  \href{https://github.com/phelipetls/}{\faIcon[solid]{github} phelipetls}
}
\smallskip

\section*{EXPERIENCE}

\textbf{\href{https://www.bornlogic.com}{Bornlogic}} \hfill Aug. 2020 -- Present \\
\textit{Desenvolvedor front-end Pleno} \hfill \textit{Remoto} {\parfillskip=0pt\par}

\begin{tightlist}
  \item Helped maintain and improve a web app made with \emph{create-react-app}
    and written in \emph{JavaScript}.
  \item Implemented a new Design System, made from scratch with TypeScript and
    styled-components, collaborating closely with the design team by using
    Storybook and Chromatic.
\end{tightlist}

\textbf{\href{https://mutual.club}{Mutual}} \hfill Dez. 2020 -- Aug. 2022 \\
\textit{Front-end developer} \hfill \textit{Remote} {\parfillskip=0pt\par}

\begin{tightlist}
  \item Developed web apps with React, TypeScript, create-react-app and Next.js.
  \item Developed mobile apps with React Native, using react-native-cli and Expo
    bare workflow.
  \item Integrated mobile and web apps with SDKs for marketing, analytics,
    notifications, feature flags, error monitoring and more.
  \item Wrote integration tests for mobile and web apps with Cypress and
    react-testing-library.
\end{tightlist}

\section*{SKILLS}

\begin{description}
  \item[Programming languages] JavaScript, TypeScript, Python, Bash, Lua.
  \item[Front-end] React, React Native, Next.js, create-react-app, Storybook,
    Jest, react-testing-library, Mock Service Worker, webpack, Vite, MUI, Redux,
    react-query, emotion, Tailwind CSS.
  \item[Back-end] Express, Koa, Flask, MongoDB, PostgreSQL.
  \item[DevOps] Docker, GitLab CI/CD, GitHub Actions, Ansible.
  \item[Project management] ClickUp, Scrum, Agile, GitHub Issues.
\end{description}

\section*{EDUCATION}

\textbf{Universidade Federal Rural do Rio de Janeiro} \hfill {Mar. 2015 -- Dec. 2020} \\
\textit{Economics} \hfill \textit{Seropédica, RJ} {\parfillskip=0pt\par}

\section*{LANGUAGES}

\begin{tightlist}
  \item Advanced English.
\end{tightlist}

\end{document}
